The Globular Cluster System of the Auriga Simulations

### 2019-05-23 AurigaGCS.tex
Wrote some discussion

% Abstract of the paper
\begin{abstract}
\todo[inline]{Rob Grand: `for many Auriga papers Carlos Frenk and Adrian Jenkins
are offered co-authorship. Perhaps you could ask Simon about this.'}
We investigate whether the galaxy formation model used for the Auriga simulations
can produce a realistic globular cluster population at redshift zero. We compare
properties of the simulated star particles in the Auriga haloes with
catalogues of observations of the Milky Way globular cluster population available
in the literature. We find that the Auriga simulations do produce sufficient mass
at radii and metallicities that are typical for the MW GCS, although we observe
a varying mass-excess for the different $R_{\text{GC}}$-[Fe/H] bins. This implies
different values for the combined product of the bound cluster formation efficiency
and the globular cluster disruption rate. We investigate whether these differences
could result from formation insitu vs. accreted star particles. We find ... TODO.
Furthermore we test whether any of the Auriga galaxies has a metallicity and radial
distribution that is consistent with the MW (M31) GCS. For all of the Auriga haloes
we reject the null hypothesis that the simulated and observed metallicities are
drawn from the same distribution at $\geq98.32$~\% confidence level, for the GCS
of the Milky Way as well as that of the Andromeda galaxy. The same holds true for
the distribution of galactocentric radius.
\end{abstract}

@@

\section{Introduction}
Globular clusters (GC)s are omnipresent, bright, old, and amongst the simplest
stellar configurations in the Universe. The globular cluster systems (GCS) of
the Milky Way (MW) and the Andromeda galaxy (M31) have been studied extensively 
over the last decades. More recent analyses of the Gaia data shed new light on the 
chemical- and structural properties, and on the phase-space distribution 
of the MW GC system.
% https://arxiv.org/abs/1805.01408
% https://arxiv.org/abs/1807.09775
% https://www.aanda.org/articles/aa/abs/2018/08/aa32698-18/aa32698-18.html
Moreover, the visbility and ubiquity of GCs makes it possible to obtain integrated 
properties of GCs within the Local Group with reasonable certainty, and even of 
those that are located further away within the Virgo Supercluster.

The natal gas regions in which globular clusters form inherit key characteristics 
from their parent (proto-)galaxies. GC populations, in turn, will therefore retain 
a record of these properties and offer unique insight into the detailed chemical 
and dynamical evolution history of their host galaxies. In theory, this information 
should be readily available and easily observable in the low redshift Universe, given 
that GCs survive nearly a Hubble time of evolution within the violent galactic 
environments they live in. However, these long and complex evolution histories
themselves imposes their imprints onto the GCs observables. Thus, a prerequisite to 
infer galactic histories from studies of GC systems is to understand the 
subtleties of the GC formation and evolution itself.

The literature offers several formation scenerarios that are consistent with the 
data. One important constraint comes from bimodality in the colour distribution, 
which is indicative of a bimodality in the underlying metallicity distribution 
of GC systems. For example, GCs in the MW are typically split up in a metal-rich 
(red) and metal-poor (blue) subpopulation divided at [Fe/H]~$=-1$ 
\citep[e.g.][]{Harris2001}. These two subpopulations could be associated to the 
galactic disk, respectively to the stellar halo \citep[e.g.][]{1985ApJ...293..424Z}. 
The latter is supported by observed similarities between the spatial distribution
and chemical signature of the `blue' GCs and the Galactic stellar halo 
\citep{2008A&ARv..15..145H}. Moreover, relative age-estimates indicate that the 
metal-poor subpopulation may be $1.5$~Gyr younger than the metal-rich counterpart 
\citep{2005AJ....130..116D}, providing futher support that the GC population indeed
consists of two distinct classes.

@@

\citet{2006ARA&A..44..193B} for a review of extragalactic GCs and galaxy
formation.

@@

The Auriga suite has a fiducial resolution level L4, accompanied by the lower
(higher) level L5 (L3) that is available for selected initial condition runs.
The baryonic mass resolution in order of increasing level is $m_b$~=~[$4 \times 10^5$,
$5 \times 10^4$, $6 \times 10^3$]~M\Sun \, with gravitational softening of
collissionless particles $\epsilon$~=~[$738, 369, 184$]~pc.

@@

We find that the age cut lowers the mean metallicity from \textasciitilde{}$0.0$
to \textasciitilde{}$-0.6$.
Furthermore, the old accreted stars generally have lower metallicities than the
old insitu stars. The difference between the mean metallicity of the old insitu 
and old accreted stars for the majority of the simulations is \textasciitilde{}$0.3$ (e.g.
\mbox{Au4-21}), and \textasciitilde{}$0.5$ dex for \mbox{Au4-10}, \mbox{Au4-16}, \mbox{Au4-17},
\mbox{Au4-18} and \mbox{Au4-22}. This trend is only reversed for \mbox{Au4-1}
and \mbox{Au4-4}, for which the old insitu population has a lower mean metallicity 
instead. For \mbox{Au4-1} we find $\mu = -1.51$ (-0.74) for the old insitu (accreted), 
but the former consists of only $1019$ particles ($1.3$\% of all GC candidates, and 
with a total mass of 5e7 M\Sun) thus we believe our classification of insitu is 
flawed for this halo due to misclassification of the primary halo in the merger
tree by subfind. For \mbox{Au4-4}, $10.8$ \% of the GC candidates is classified 
as insitu (compared to insitu fractions of $40-80$\% for other haloes). Overall
we find that the simulations produce (sub)populations of GC candidates that are
more metal-rich than the MW and M31 GC systems. Moreover, none of the simulations
has a population of GC candidates with a bimodal metallicity distribution
(the green curves).

@@

We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma}. The green crosses are to be compared to the 
purple (magenta) cross, which shows the mean value of all MW (M31) GCs. 
We test the null hypothesis that MW (M31) and the GC candidates (all, insitu, and
accreted) are drawn from the same underlying distribution by calculating the KS
test statistic (i.e. six KS tests per simulation). We reject $H_0$ at the 100.00~\%
confidence level for virtually all subsets of all simulations, both for MW and M31,
except when comparing the old accreted stars of \mbox{Au4-10} to the MW GCS. In this 
case we still reject $H_0$ with, but with $\leq 98.68$~\% confidence. When comparing
to the M31 GCS, the `best' matches are the old accreted subpopulations of \mbox{Au4-13},
\mbox{Au4-15}, and \mbox{Au4-17} ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%, 
and 98.32~\%). Here we find that the cumulative distributions are more or less 
similar up to [Fe/H]~\textasciitilde{}$-0.5$, above which the simulations yield higher number 
counts which drives the KS test statistic over the critical values. This affirms
our finding that the simulations produce GC candidates that are more metal-rich 
than the MW (M31) GCS. The main reason reasons that $H_0$ is rejected with such 
high confidence are under-production of old stars with [Fe/H]~$\leq$~-1.5,
and over-production of stars with [Fe/H]$\geq$~-0.5.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the total mass in GC candidates produced by the Auriga simulations. 
We show the median (coloured lines) for all thirty Auriga L4 haloes with the 
$1\sigma$ interval around it (shaded regions, which shows the scatter between 
runs that have different initial conditions, thus, have unique merger histories). 
We chose to aggregate the data to indicate a general trend that we find when the
GC candidates are split up according to birth location, rather than selecting 
typical examples of individual galaxies. Figure~\ref{fig:FeH} shows the mass-weighted
metallicity distribution of all Auriga L4 galaxies. Once again we notice that the 
peak metallicity shifts down from $0$ to $-0.5$ for old stars (green solid)
compared to all stars (green dotted), and we learn that the mass at the peak 
lowers by roughly one dex. The mass budget of the old stars is dominated by the 
old insitu population (blue solid) below [Fe/H]~=~$-1$, and by the old accreted 
stars (red solid) above this value. We show the MW (M31) GCS in purple (magenta) 
and we show the ratio of the simulated to the observed profiles in the middle 
(bottom) panel. This mass excess can be thought of the `mass budget' that the
Auriga GC candidates can `afford to lose' due to a combination of smaller than
unity bound cluster formation efficiencies combined with a Hubble time of dynamical 
evolution, while still producing a GC system with sufficient mass to be consistent
with the MW (M31) GCS. The cluster formation efficiency would have to linearly
decrease with decreasing metallicity for Auriga GC candidates to produce a population
of GC candidates that is consistent with the MW. For the GC candidates in M31
we find a constant mass excess up to \textasciitilde{}$-0.9$, above which the 
simulations produce a higher mass excess with increasing metallicity. If dynamical
evolution is not expected to more efficiently disrupt GCs of higher metallicity,
then we would find that the efficiency to form bound star clusters would have to
decrease with increasing metallicity.

@@

\section{Discussion}
\label{sec:discussion}
\subsection{Metallicity distribution}
\label{sec:discussion_FeH}
\citet[][p. 234]{1998gcs..book.....A} and \citet[][p. 38]{Harris2001} describe
the bimodal [Fe/H] distribution of the MW GCS. The latter fits a double
Gaussian that peaks at [Fe/H] = $-1.59$ (metal-poor) and $-0.51$ (metal-rich)
with dispersions of $0.34$ and $0.23$. T
KMM mixture-modeling

Furthermore, 
We note that the scatter between different
Auriga haloes is much smaller than the difference between the MW and M31 GCSs.
We conclude that old star particles in the Auriga simulation suite as a whole
cannot be consistent with both the Milky Way and the Andromeda globular cluster
system.

We observe an increasing trend with increasing metallicity
for the Milky Way over the entire range of the data, while the M31 GCS shows
this increase only in the range [Fe/H]$>$-0.5 (although not for the \emph{old
accreted} component.

Furthermore we test the null hypothesis that the metallicity distribution of the
MW (M31) GCS and the \emph{old}, \emph{old insitu}, and \emph{old accreted} star
particles in the Auriga simulations are drawn from the same underlying
distribution. We calculate the two-sample Kolmogorov-Smirnov test statistic for
all thirty Auriga level 4 haloes and reject the null hypothesis for every halo,
for every sub set of star particles at least at the 99.99\% confidence level.
In addition, the null hypothesis that the metallicity distributions of the MW
and M31 GCS are drawn from the same distribution is rejected at the 99.99997\%
confidence level.

\subsection{Radial distribution}
\label{sec:discussion_Rgc}

\todo[inline]{
    Harris: `Somewhat arbitrarily, I will take the region $r_p > 3$ kpc
    (containing 75 clusters) as the fiducial Milky Way sample. If we were to
    view the Milky Way at the same inclination angle to the disk as we see
    M31, this cutoff in projected distance would correspond roughly to the
    inner distance limits in the M31 halo sample.'
}

\subsection{Metallicity-radial space}
\label{sec:discussion_FeHRgc}
See Figure~\ref{fig:observations_FeHRgc} in Sec.~\ref{sec:observations_FeHRgc}.

\todo[inline]{
``The fraction of all star formation that occurs in bound stellar clusters (the cluster formation efficiency, hereafter CFE) follows by integration of these local clustering and survival properties over the full density spectrum of the ISM, and hence is set by galaxy-scale physics. We derive the CFE as a function of observable galaxy properties, and find that it increases with the gas surface density'' \citep{2012MNRAS.426.3008K}
}

\subsection{Age cut}
Although the age distribution of M31 Perhaps an age cut of 6~Gyr would would be more
appropriate for M31, see Figure~\ref{fig:MW-M31-age}.

\todo[inline]{
\citet{2016ApJ...824...42C} writes:
``there are two broad, well-established differences:
(1) the M31 GC system is more populous than the MW system, by a factor of
$\sim$2-3, and (2) it does not exhibit the same obvious bimodality in
metallicity \citep{2000AJ....119..727B, 2009A&A...508.1285G, 2011AJ....141...61C,
2013A&A...549A..60C}. Both of these aspects may be reflections of dramatic
differences discovered in these galaxies stellar halos, where the M31 halo
appears much more metal-enriched, with massive substructures suggesting a more
active satellite accretion history \citep[e.g.][]{2009Natur.461...66M}''
}

\subsection{From star particles to globular clusters}
\label{sec:discussion_mass_excess}
Star particles are not globular clusters. Many stars do form in clusters, but
not all clusters end up gravitationally bound. Star particles in the
Auriga simulations represent single-age stellar populations that have formed
at the same location within the galaxy. Therefore one could assume a model
for the star cluster formation efficiency $\Gamma$, which could be used to
`convert' star particles to bound star clusters e.g. Kruijssen (2012). This
model relies on the local birth properties of the star particles. However,
in our analysis we can retrieve the properties of the star particle in the
first snapshot it was recorded, but not the gas properties at times of birth.
Therefore we are unable to model the formation of star clusters in more detail.

Furthermore, we compare star particles to present-day globular clusters, thereby
ignoring the effects of (dynamical) disruption of globular clusters over nearly
a Hubble time. As shown by Pfeffer et al. (2018), a detailed model of the tidal
history of star clusters requires a temporal resolution of order mega year. For
the Auriga level 4 simulations we have 128 snapshots for the age of the Universe,
thus, a far too coarse temporal resolution for meaningful calculations.

Therefore we investigate the over-production of simulated mass in the metallicity
and radial bins and use the term `efficiency' to refer to the combined product
of bound cluster formation and globular cluster disruption. In Figure~\ref{fig:todo}
we show the efficiencies that we find when we compare the simulations to the
globular cluster systems of the Milky Way as well as that of Andromeda (M31).

@@

>>>>

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy formation model used for the Auriga simulations
can produce a realistic globular cluster population at redshift zero. We compare
properties of the simulated star particles in the Auriga haloes with catalogues 
of observations of the Milky Way and Andromeda globular cluster populations available
in the literature. We find that the Auriga simulations do produce sufficient mass
at radii and metallicities that are typical for the MW GCS, although we observe
a varying mass-excess for the different $R_{\text{GC}}$-[Fe/H] bins. This implies
different values for the combined product of the bound cluster formation efficiency
and the globular cluster disruption rate. Furthermore we test whether any of the
Auriga galaxies has a metallicity and radial distribution that is consistent with
the MW (M31) GCS. For all of the Auriga haloes we reject the null hypothesis that
the simulated and observed metallicities are drawn from the same distribution at
$\geq98.32$~\% confidence level, for the GCS of the Milky Way as well as that of
the Andromeda galaxy. The same holds true for the distribution of galactocentric 
radius. Overall, the Auriga simulations produce old star particles with higher
metallicities than the MW and M31 GCS and at larger radii. The formation efficiency
would have to linearly decrease with increasing metallicity for the Auriga GC
candidates to be consistent with the MW GCS.
\end{abstract}

@@

\section{Introduction}
Globular clusters (GC)s are omnipresent, bright, old, and amongst the simplest
stellar configurations in the Universe. The globular cluster systems (GCS) of
the Milky Way (MW) and the Andromeda galaxy (M31) have been studied extensively 
over the last decades. More recent analyses of the Gaia data shed new light on the 
chemical- and structural properties, and on the phase-space distribution 
of the MW GC system \citep[e.g.][]{2018A&A...616A..12G, 2018ApJ...859L..13B,
2019A&A...621A..56P, 2019MNRAS.484.2832V}. Moreover, the visbility and ubiquity
of GCs makes it possible to obtain integrated properties of GCs within the Local 
Group with reasonable certainty, and even beyond the Local Group \citep[e.g.][]{1991ARA&A..29..543H}.

The natal gas regions in which globular clusters form inherit key characteristics 
from their parent (proto-)galaxies. GC populations, in turn, will therefore retain 
a record of these properties and offer unique insight into the detailed chemical 
and dynamical evolution history of their host galaxies \citep[see][for a recent review]
{2006ARA&A..44..193B}. In theory, this information should be readily available
and easily observable in the low redshift Universe, given that GCs survive nearly
a Hubble time of evolution within the violent galactic environments they live in. 
However, these long and complex evolution histories themselves impose their
imprints onto the GCs observables. Thus, a prerequisite to infer galactic histories
from studies of GC systems is to understand the subtleties of the GC formation
and evolution itself.

One important ingredient for plausible formation mechanisms comes from observed 
bimodality in the colour distribution, believed to be indicative of bimodality
in the underlying metallicity distribution of GC systems. GCs in the MW can 
be split up into a metal-rich (red) disk, and a metal-poor (blue) halo
(sub)population. The exact dividing value slightly differs between authors,
e.g. [Fe/H]~$=-0.8$ \citep[according to][]{1985ApJ...293..424Z}, or
[Fe/H]~$=-1.0$ \citep[according to][]{Harris2001}, and may also differ between
\newpage
galaxies \citep[e.g.][]{1985ApJ...293..424Z, 1999AJ....118.1526G, 2001AJ....121.2974L,
2006ApJ...639...95P}. It has long been debated whether the Andromeda GCS metallicity 
distribution is uni- bi- or multimodal, with \citet{2016ApJ...824...42C} recently
arguing that the data favours three groups (split at [Fe/H] $= -0.4$ and $-1.5$)
after more accurate age-measurements improved classification of star clusters
as globular (or otherwise).

The literature offers several formation scenarios.

The latter is supported by observed similarities between the spatial distribution
and chemical signature of the `blue' GCs and the Galactic stellar halo 
\citep{2008A&ARv..15..145H}. Moreover, relative age-estimates indicate that the 
metal-poor subpopulation may be $1.5$~Gyr younger than the metal-rich counterpart 
\citep{2005AJ....130..116D}, providing further support that the GC population indeed
consists of two distinct classes.

@@

\citet{2010MNRAS.404.1203F} collected age-metallicity observations from the
literature and found one track with constant age of 12.8~Gyr, and one track
with branches towards younger ages. These branches are dominated by GCs associated 
with the Sagittarius, Canis Major and other accreted dwarf galaxies, ultimately
indicating that 27-47 GCs (about one 25\% of the MW GCS) have been accreted
from six to eight dwarf galaxies. \citet{2019MNRAS.486.3134K, 2019MNRAS.486.3180K}
show that GC simulated age-metallicity space of the E-MOSAICS suite indeed allows 
for a reconstruction of the merger history of the Milky Way-like galaxies, and 
conclude that 40\% of the MW GCS has been accreted from galaxies with a stellar
mass range of $2 \cdot 10^{7} - 2 \cdot 10^{9}$ M\Sun, and $6\pm1$ are core remnants
of accreted dwarfs.

@@

The Auriga suite has a fiducial resolution level L4, accompanied by the lower
(higher) level L5 (L3) that is available for selected initial condition runs.
The baryonic mass resolution in order of increasing level is $m_b$~=~[$4 \times 10^5$,
$5 \times 10^4$, $6 \times 10^3$]~M\Sun \, with gravitational softening of
collissionless particles $\epsilon$~=~[$738, 369, 184$]~pc. The mass resolution
of the Auriga simulations is thus close to the characteristic peak mass of the
lognormal GC mass distribution of $10^{5}$~M\Sun \citep{1991ARA&A..29..543H}, 
although the gravitational softening is two orders of magnitudes larger than
typical GC radii. High-density gaseous regions are thus not expected to produce
surviving stellar clumps (GCs) with masses and radii consistent with GCs because
such objects would numerically disperse, even in the highest-resolution runs.
On the other hand, we can investigate (statistical) properties of age-selected 
GC candidates because each star particle represents a single stellar population
with a total mass that could be consistent with one globular cluster.

@@

We find that the age cut lowers the mean metallicity from $0.0$ to $-0.6$.
Furthermore, the old accreted stars generally have lower metallicities than the
old insitu stars. The difference between the mean metallicity of the old insitu 
and old accreted stars for the majority of the simulations is \textasciitilde{}$0.3$ (e.g.
\mbox{Au4-21}), and \textasciitilde{}$0.5$ dex for \mbox{Au4-10}, \mbox{Au4-16}, \mbox{Au4-17},
\mbox{Au4-18} and \mbox{Au4-22}. This trend is only reversed for \mbox{Au4-1}
and \mbox{Au4-4}, for which the old insitu population has a lower mean metallicity 
instead. For \mbox{Au4-1} we find $\mu = -1.51$ (-0.74) for the old insitu (accreted), 
but the former consists of only $1019$ particles ($1.3$\% of all GC candidates, and 
with a total mass of 5e7 M\Sun) thus we believe our classification of insitu is 
flawed for this halo due to misclassification of the primary halo in the merger
tree by subfind. For \mbox{Au4-4}, $10.8$ \% of the GC candidates is classified 
as insitu (compared to insitu fractions of $40-80$\% for other haloes). Overall
we find that the simulations produce (sub)populations of GC candidates that are
more metal-rich than the MW and M31 GC systems. Moreover, none of the simulations
has a population of GC candidates with a bimodal metallicity distribution
(the green curves).

@@

We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma}. The green crosses are to be compared to the 
purple (magenta) cross, which shows the mean value of all MW (M31) GCs. 
We test the null hypothesis that MW (M31) and the GC candidates (all, insitu, and
accreted) are drawn from the same underlying distribution by calculating the KS
test statistic (i.e. six KS tests per simulation). We reject $H_0$ at the 100.00~\%
confidence level for virtually all subsets of all simulations, both for MW and M31,
except when comparing the old accreted stars of \mbox{Au4-10} to the MW GCS. In this 
case we still reject $H_0$ with, but with $\leq 98.68$~\% confidence. When comparing
to the M31 GCS, the `best' matches are the old accreted subpopulations of \mbox{Au4-13},
\mbox{Au4-15}, and \mbox{Au4-17} ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%, 
and 98.32~\%). Here we find that the cumulative distributions are more or less 
similar up to [Fe/H]~$-0.5$, above which the simulations yield higher number 
counts which drives the KS test statistic over the critical values. This affirms
our finding that the simulations produce GC candidates that are more metal-rich 
than the MW (M31) GCS. The main reason reasons that $H_0$ is rejected with such 
high confidence are under-production of old stars with [Fe/H]~$\leq$~-1.5,
and over-production of stars with [Fe/H]$\geq$~-0.5.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the total mass in GC candidates produced by the Auriga simulations. 
We show the median (coloured lines) for all thirty Auriga L4 haloes with the 
$1\sigma$ interval around it (shaded regions, which shows the scatter between 
runs that have different initial conditions, thus, have unique merger histories). 
We chose to aggregate the data to indicate a general trend that we find when the
GC candidates are split up according to birth location, rather than selecting 
typical examples of individual galaxies. Figure~\ref{fig:FeH} shows the mass-weighted
metallicity distribution of all Auriga L4 galaxies. Once again we notice that the 
peak metallicity shifts down from $0$ to $-0.5$ for old stars (green solid)
compared to all stars (green dotted), and we learn that the mass at the peak 
lowers by roughly one dex. The mass budget of the old stars is dominated by the 
old insitu population (blue solid) below [Fe/H]~=~$-1$, and by the old accreted 
stars (red solid) above this value. We show the MW (M31) GCS in purple (magenta) 
and we show the ratio of the simulated to the observed profiles in the middle 
(bottom) panel. This mass excess can be thought of the `mass budget' that the
Auriga GC candidates can `afford to lose' due to a combination of smaller than
unity bound cluster formation efficiencies combined with a Hubble time of dynamical 
evolution, while still producing a GC system with sufficient mass to be consistent
with the MW (M31) GCS. The cluster formation efficiency would have to linearly
decrease with decreasing metallicity for Auriga GC candidates to produce a population
of GC candidates that is consistent with the MW. For the GC candidates in M31
we find a constant mass excess up to $-0.9$, above which the 
simulations produce a higher mass excess with increasing metallicity. If dynamical
evolution is not expected to more efficiently disrupt GCs of higher metallicity,
then we would find that the efficiency to form bound star clusters would have to
decrease with increasing metallicity.

@@

\section{Discussion}
\label{sec:discussion}
\subsection{Metallicity distribution}
\label{sec:discussion_FeH}
We find that the metallicity distributions of GC candidates in the Auriga
simulations are more metal-rich than the MW (M31) GCS. Although the (old) star 
particles represent single stellar populations with a mass (resolution) comparable 
to the peak of the GCMF, they are in fact statistical tracers of the stellar 
population of the galaxy as a whole. Therefore only a (small) fraction of the 
star particles may represent plausible formation sites of GCs, whereas the majority
represent (halo) field stars - the disk component effectively falls outside
our selection of star particles due to the age cut. Globular clusters are 
$\sim$~$0.5$ dex more metal-poor than spheroid stars observed at the same radius
for almost all galaxies \citep{1991ARA&A..29..543H}. Our finding that star particles older 
than 10~Gyr have higher metallicities than the MW (M31) GCS may simply be a 
reflection thereof.

\citet[][p. 234]{1998gcs..book.....A} and \citet[][p. 38]{Harris2001} quantify
the bimodality of the [Fe/H] distribution of the MW GCS, the latter fit a double
Gaussian which peaks at [Fe/H] = $-1.59$ (metal-poor) and $-0.51$ (metal-rich)
and dispersions of $0.34$ and $0.23$. However, the metallicity distribution of 
GC candidates in the Auriga simulations is not bimodal, although an offset between
the mean values does emerge when further splitting them up according to birth location 
(accreted or in-situ). The majority of the simulations show an offset in the mean 
values of roughly $0.3$~dex between both subpopulations, while a small number of 
simulations has an offset of order $0.5$~dex. Our finding that the mean values of 
the old insitu GC candidates are roughly consistent with the metal-rich MW GCs 
could be interpreted as an indication that this subpopulation may have formed 
in-situ. However, we also notice that a substantial number of simulations has
similar mean values for all GC candidates, and the simulated insitu GC candidates 
have larger dispersions than the metal-rich GCs. Moreover, the offset between the 
mean of the metal-rich and metal-poor populations in the MW is $1$ dex, a factor 
$2-3$ larger than the offset we find between the insitu and accreted populations. 
The simulations are not consistent with the picture that all metal-rich GCs 
formed insitu and that all metal-poor GCs were accreted.

\citet{2006ARA&A..44..193B} compare the number of metal-poor GCs to the stellar
halo mass and find\footnote{the quantity $T$ is the number of GCs per $10^9$ M\Sun \,
of galaxy stellar mass} $T^n_{\text{blue}} \sim 100$, while the
number of metal-rich GCs compared to the bulge mass yields $T^n_{\text{red}} \sim 5$,
and therefore conclude that the formation efficiency of metal-poor GCs is
twenty times higher than the metal-rich GCs with respect to field stars.

% Interestingly, the cross-over point above (below) which the mass-weighted 
% metallicity distribution of GC candidates is dominated by those that have
% formed insitu (were accreted) coincides with the separation between the metal-rich
% and metal-poor population for the MW GCS at [Fe/H]~=~$-1$.

\subsection{Radial distribution}
\label{sec:discussion_Rgc}
The M31 GCS has a factor 2-3 more GCs at large radii compared to the MW GCS,
which may indicate that M31 has a richer merger history than the MW. In the 
Auriga simulations we find that the GC candidates at radii larger than 
$\sim20$~kpc are indeed dominated by accreted star particles. However, we select
star particles that are bound to the main halo and main subhalo, which means that
we include particles up to the virial radius $R_{200}$. The Auriga simulations 
have no problem populating the stellar halo up to the virial radius, even with 
our additional age cut. On the other hand, the MW and M31 have fewer GCs at large
radii. We expect tidal disruption to be less efficient at larger radii, thus, 
the formation efficiencies of the accreted GC candidates would have to be lower.
Our classification as GC candidates could, for example, be improved by selecting
a number of globular clusters based on the $M_{vir}-N_{\text{GC}}$ correlation
found by \citet{2019arXiv190100900B}, and taking a virial mass below which none
of the star particles is treated as GC candidate.

% \todo[inline]{
%     Harris: `Somewhat arbitrarily, I will take the region $r_p > 3$ kpc
%     (containing 75 clusters) as the fiducial Milky Way sample. If we were to
%     view the Milky Way at the same inclination angle to the disk as we see
%     M31, this cutoff in projected distance would correspond roughly to the
%     inner distance limits in the M31 halo sample.'
% }

\subsection{Star particles are not globular clusters}
\label{sec:discussion_mass_excess}
A major improvement to our classification of star particles as GC candidates
could be made by explicitly taking into the formation efficiency of bound star 
clusters \citep{2012MNRAS.426.3008K}, which depends on the local ISM properties
(density, pressure, sound speed). However, the only information available in 
post-processing are the properties of the star particles recorded in the first 
snapshot after formation. We could attempt to obtain the properties of the nearest
gas cell, but this would have to be limited to a very narrow time window between
the time of formation and the time of the snapshot because the star particle could 
otherwise be in a completely different location than where it was born initially. 
Moreover, even if the birth time and snapshot time would coincide, it would not
be obvious that the gas cell will yield the correct quantities as the formation
of the star itself alters the properties of the gas. We therefore did not further
attempt a more sophisticated modeling of the cluster formation efficiency in
post-processing.

Furthermore, we compare star particles to present-day globular clusters, thereby
ignoring the effects of (dynamical) disruption of globular clusters over nearly
a Hubble time. As shown by \citep{2018MNRAS.475.4309P}, a detailed model of the tidal
history of star clusters requires a temporal resolution of order mega year. For
the Auriga L4 simulations we have a total of 128 snapshots available over the
age of the Universe, thus, far too coarse temporal resolution for meaningful 
calculations of tidal disruption along the orbit of our GC candidates. Therefore 
we can only combine these two shortcomings of our analysis into the `mass excess',
which includes the cluster formation efficiency and consecutive globular cluster 
disruption.

% \todo[inline]{
% \citet{2019MNRAS.486.3134K} ``Due to the multitude of low-mass progenitors and 
% rapid merging during this early phase of galaxy growth, we recommend to reserve
% the term `ex situ GCs' for accretion events taking place at $z < 2$, when the
% central spheroid has formed and accretion events unambiguously contribute to the
% spatially extended (`halo') GC population.''
% }
% 
% 
% \citet{2016ApJ...824...42C}
% ``We find that the clusters can be divided into three major metallicity groups 
% based on their radial distributions: (1) an inner metal-rich group ([Fe/H] $> -0.4$);
% (2) a group with intermediate metallicity (with median [Fe/H] $= -1$); and (3) 
% a metal-poor group, with [Fe/H] $< -1.5$.''
% 
% \citet{2016ApJ...824...42C}
% ``Although this disk mode of GCs is intriguing, the very dominant subpopulations 
% in M31 are the lower-metallicity GCs. It seems likely that these objects were 
% brought in by the accretion of satellite galaxies (minor mergers). The populous
% GC system of M31, relative to the MW, would then reflect a more active accretion
% history, and the radial gradient of GC metallicities could arise through 
% correlations of both metallicity and dynamical friction with satellite galaxy
% mass (e.g., Amorisco 2016).''

@@

We investigate GC candidates in the Auriga simulations and draw the following
conclusions.

\begin{itemize}
    \item The star formation model implemented in the Auriga simulations produces
    metallicity distributions that are more metal-rich the Milky Way and M31 
    globular cluster systems.
    \item We reject the null hypothesis $H_0$ that MW (M31) and the GC candidates
    (all, insitu, and accreted) are drawn from the same underlying distribution
    for all Auriga L4 galaxies with $\geq 98.68$~\% confidence.
    \item GC candidates in the Auriga simulations may be found out to $R_{200}$,
    given our selection function of star particles selects all stars bound to the
    main subhalo in the main halo. The stellar mass is dominated by accreted star
    particles at radii beyond $20$~kpc The GCs in the MW and M31, on the other hand,
    have a much smaller radial extend. 
    \item The cluster formation efficiency would have to increase with decreasing
    metallicity for GC candidates in the Auriga simulations to be consistent
    with the Milky Way GC system, given that we expect dynamical evolution to more strongly affect GC
    candidates at smaller radii.
    \item The Auriga simulations are not consistent with the picture that all 
    metal-rich GCs formed insitu and that all metal-poor GCs were accreted.
\end{itemize}
